Supporting Information : Complex, informative, and previously ignored dependencies propogate throughout ecology and can be revealed using copulas

### 2019-05-10 SupportingInformation.Rmd
editing to address Drake comments at presubmission

---
title: "Supporting Information : The importance of a complete description of dependence between variables for ecology and related fields"
author: "Shyamolina Ghosh, Lawrence W. Sheppard, Mark T. Holder, Terrance E. Loecke, Philip C. Reid, James D. Bever, Daniel C. Reuman"
geometry: "left=1cm,right=1cm,top=2.2cm,bottom=2.2cm"

@@

# Transformations used in Fig. \ref{MT-fig_cop_pedag1} \label{pedagog1_details}

The data of Fig. \ref{MT-fig_cop_pedag1}A-B were generated to have standard normal marginals.
Fig. \ref{MT-fig_cop_pedag1}C can be obtained from Fig. \ref{MT-fig_cop_pedag1}A via transformation
of both variables by the cdf of the standard normal distribution, and then by the inverse of 
the cdf of the gamma distribution with shape and scale parameters 2. 
The function `qgamma` in R was used.
Fig. \ref{MT-fig_cop_pedag1}D can be obtained from Fig. \ref{MT-fig_cop_pedag1}B in the same way.
Fig. \ref{MT-fig_cop_pedag1}E can be obtained from Fig. \ref{MT-fig_cop_pedag1}A via transformation
of both variables by the cdf of the standard normal distribution.
Fig. \ref{MT-fig_cop_pedag1}F can be obtained from Fig. \ref{MT-fig_cop_pedag1}B in the same way.

>>>>

---
title: "Supporting Information : Complex, informative, and previously ignored dependencies propogate throughout ecology and can be revealed using copulas"
author: "Shyamolina Ghosh, Lawrence W. Sheppard, Mark T. Holder, Terrance E. Loecke, Philip C. Reid, James D. Bever, Daniel C. Reuman"
geometry: "left=1cm,right=1cm,top=2.2cm,bottom=2.2cm"

@@

# Transformation alters Pearson but not Spearman correlation \label{pedagog1_details}

The data of Fig. \ref{MT-fig_cop_pedag1}A-B were generated to have standard normal marginals.
Fig. \ref{fig_transf_pearson_spearman}A can be obtained from Fig. \ref{MT-fig_cop_pedag1}A via transformation
of both variables by the cummulative distribution function (cdf) of the standard normal distribution, and then by the inverse of 
the cdf of the gamma distribution with shape and scale parameters 2. 
The functions `pnorm` and `qgamma` in R were used.
Fig. \ref{fig_transf_pearson_spearman}B can be obtained from Fig. \ref{MT-fig_cop_pedag1}B in the same way.
The Pearson correlations differ substantially after transformation, 
but the Spearman correlations are unchanged (Figs \ref{MT-fig_cop_pedag1}A-B, \ref{fig_transf_pearson_spearman}).
Fig. \ref{MT-fig_cop_pedag1}C (the points, not the contours) can be obtained from Fig. \ref{MT-fig_cop_pedag1}A via transformation
of both variables by the cdf of the standard normal distribution.
Fig. \ref{MT-fig_cop_pedag1}D can be obtained from Fig. \ref{MT-fig_cop_pedag1}B in the same way.

\begin{figure}[!h]
\begin{center}
\includegraphics[width=10 cm]{./Results/PedagogFig_SMExport.pdf}
\caption[Transformation alters Pearson but not Spearman correlation]{Transformation alters Pearson but not Spearman correlation. 
Displayed data are transformed from the data pictured on
Fig. \ref{MT-fig_cop_pedag1}A-B. See Appendix \ref{pedagog1_details} for 
details. P=Pearson, S=Spearman 
correlation.\label{fig_transf_pearson_spearman}}
\end{center}
\end{figure}
